Scientific Team Project

### 2018-04-23 Presentations/Milestone1/presentation.tex
Add literature research

>>>>

\section{Literature Research}
\begin{frame}
\frametitle{Literature Research}
\begin{itemize}
	\item Xu, Dongping, and Brett Bode. \emph{"Performance study and dynamic optimization design for thread pool systems".} Diss. United States. Department of Energy. Office of Science, 2004.
	\item Ling, Yibei, Tracy Mullen, and Xiaola Lin. \emph{Analysis of optimal thread pool size.} ACM SIGOPS Operating Systems Review 34.2 (2000): 42-55.
	\item Kang, DongHyun, et al. \emph{Prediction-based dynamic thread pool scheme for efficient resource usage.} Computer and Information Technology Workshops, 2008. CIT Workshops 2008. IEEE 8th International Conference on. IEEE, 2008.
\end{itemize}
\end{frame}
